### 2025-09-15 paper/fig/natural-language-forms.tex

        Numerical value
        & the training time per epoch growing from \hl{67} seconds to 106 seconds.
        &
        \begin{lstlisting}[language=Fluid,numbers=none]
(findWithKey_ "model" "LSTM" tableData).time_s
        \end{lstlisting}
        \\
        Percentage &
        The Energy Sector accounts for total methane emissions of \hl{52.80\%} in 2030.
        &
        \begin{lstlisting}[language=Fluid,numbers=none]
(record.emissions /
 sum (map (fun x -> x.emissions)
          (getByYear year tableData))) * 100

@@

        Comparison
        & The training time per epoch \hl{growing} from 67 seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
trendWord
 (findWithKey_ "model" "BiLSTM" tableData).time_s
 (findWithKey_ "model" "LSTM" tableData).time_s
 growShrink
        \end{lstlisting} \\
        Graded adjective*            & \hl{extremely likely} to be exceeded in the 20th century               & ~                             \\
        Reference to visual element*                            & ~                & ~                             \\
        \hline
    \end{tabular}
    \caption{Quantitative/semi-quantitative natural language forms considered in this paper}
    \label{tab:fluid_examples}
\end{table}

>>>>

        Numerical value
        & the training time per epoch growing from \hl{67} seconds to 106 seconds.
        &
        \begin{lstlisting}[language=Fluid,numbers=none]
(findWithKey' "model" "LSTM" tableData).time_s
        \end{lstlisting}
        \\
        Percentage &
        The Energy Sector accounts for total methane emissions of \hl{52.80\%} in 2030.
        &
        \begin{lstlisting}[language=Fluid,numbers=none]
(record.emissions /
 sum (map (fun x -> x.emissions)
          (getByYear year tableData))) * 100

@@

        Comparison
        & The training time per epoch \hl{growing} from 67 seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
trendWord
 (findWithKey' "model" "BiLSTM" tableData).time_s
 (findWithKey' "model" "LSTM" tableData).time_s
 growShrink
        \end{lstlisting} \\
        Graded adjective*            & \hl{extremely likely} to be exceeded in the 20th century               & ~                             \\
        Reference to visual element*                            & ~                & ~                             \\
        \hline
    \end{tabular}
    \caption{Quantitative/semi-quantitative natural language forms considered in this paper}
    \label{tab:fluid_examples}
\end{table}

### 2025-09-15 paper/fig/scigen-1805.02474v1-10-src.tex

\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid,mathescape=false]{../website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Source code for \figref{scigen-example-website}}
    \label{fig:fluid-example-paragraph}
\end{figure}

>>>>

\begin{figure}[h]
    \small
    % listings package seems to struggle, for now just use screenshot from VSCode
    \includegraphics[scale=0.169]{fig/scigen-1805.02474v1-10-src-screenshot.png}
    \caption{Reference solution for transparent text in \figref{scigen-example-website}}
    \label{fig:fluid-example-paragraph}
\end{figure}
